\documentclass[12pt]{article}
\usepackage{times}
\usepackage{setspace}
\doublespacing
\usepackage[margin=1in]{geometry}

\begin{document}
\title{Reflection Journal 2}
% Create a chart or list of up to five people in your life and the primary ways you communicate with them, whether via mostly rich or lean channels, or multimodality.
% Describe why your communication channels work or don’t work for these relationships.
% How could you change your communication channels so that they are richer for each of your relationships?
\par
The list of five people I interact with in my life are the following: My boss, my friend Sarah, my friend Holland, the head of the organization for Labor of Love, and my Mother. The richness and leaness of each of these relationships are very circumstantial and dynamic. My boss and I typically have a rich relationship, where I mostly ask him questions for clarification face to face. However, the relationship can move more lean via calling or texting him depending on urgency and how far away he is. My friend Holland and I typically have a lean relationship since he lives in Washington state, and we only message each other to keep in touch unless I am back home visiting where we are then in a very rich relationship, since we will go out barhopping and discussing software development. The head of the organization of \emph{Labor of Love Project}, Monica Eppinger and I also lean more so on the leaner relationships since most of the time we are messaging each other to relay information about dog and cat rescues, albeit I will go to her house every now and then to discuss something with the program. Finally, my Mother and I are really in the same circumstance as my friend Holland, since she lives in Washington State- and for the most part we just message each other unless I am back home and visiting. So I would say all of these relationships would have multimodality being they are all circumstantial.
\par
I would say mediated communication channels work the best for each of these relationships, it's the most convenient for all of us since the vast majority of my relationships live very far away, or are busy doing other things. Face to face interaction is also a solid communication channel for my relationships and I when it is feasible, since we can use body language and other subtle communication so it isn't verbal if it doesn't have to be. I don't know of any communication channels with these five relationships that don't work effectively.
\par
I don't really think there is anything I can do to change my communication channels with these relationships to be richer, or if it's even necessary. I believe that if a relationships needs to shift richer, it will do so when necessary to clarify some points and/or see people I love after not seeing them in years. If I was to attempt to enrich one of these relationships, it would either A. be far too forced, and potentially ruin a relationship, or B. I would have to move back home to be able to see some of my relationships face to face more often, which I do plan on doing eventually. It is just not feasible at the moment.

\end{document}
