\documentclass[12pt]{article}
\usepackage{times}
\usepackage{setspace}
\doublespacing
\usepackage[margin=1in]{geometry}
\begin{document}
\title{Reflection Journal 1}

%Choose one of the following and write a 1-page paper:

%Chapter 1 Journal

%Review the section titled “Characteristics of Competent Communication” (pgs. 21-23) then answer the following questions:

%    Out of the six characteristics of competent communication, which one would you identify as your single major strength in interpersonal communication? Cite two specific personal examples where you displayed this characteristic.
%   Out of the six characteristics of competent communication, which one would you identify as your one significant weakness? Give one specific example to illustrate why you feel this is a problem area for you.
%    How can you improve your weakness for face-to-face communication?
%    How can you improve your weakness as it relates to communication over social media?
\par
Out of the six characteristics of competent communication, I would say that \emph{self-monitoring} would be my single major strength. While mid conversation, I can read faces of people pretty easily to gauge whether or not they are genuinely interested in what I'm saying. When I read that I am not engaging them in conversation, or that I am beginning to sound stupid I just give up on the conversation and move on to the next one. I believe that this is important because it prevents me from wasting energy on an uninterested listener. The nice thing about self-monitoring is it allows me to be adaptable in the conversation if I want to be, especially when it comes to generational gap conversations (Upper or Lower). In order to be adaptable within conversation, however, you must first have the self-monitoring skill to be competent at the adaptable conversation. Thus in order to be a competent adaptive communicator, you must first have competent self-monitoring.
% Sarah when you edit this, we may have to break up Paragraphs even further because this assignment is confusing the shit out of me.
\par 
In person, the facial expressions and tone of someone who is engaged in the conversation is what becomes quite apparent. Body language of a listener indicating disinterest may look like: looking around for an exit, a general lack of eye contact, and forgetting what we are talking about- not being 100\% glued to the conversation, forgetting what we were talking about, it's obvious when you aren't sparking their interest. Honestly, I really don't think it has much to do with the person talking about the particular subject, I think it's the person of interest just doesn't care about that topic at that point in time at all. However, that can work to your favor since you can tell immediately if someone cares about the topic and you can either continue with the topic or just completely move on.
% Sarah, at this point I'm four whiskey sours deep and drunk off my ass, good luck with editing
\par
Online, self-monitoring is slightly more difficult depending on how much character the person of interest puts into the conversation via text. Their replies can demonstrate their emotions and reactions \emph{precisely}, or on the other hand, they have a very high difficulty putting their emotions and reactions into text. I have noticed this mostly with the Baby-Boomer generation, but also some in the Gen-Y (Millenials) and Gen-Z (Zoomer) generations. However, I absolutely love communicating like this since it requires the least amount of effort, you can do it from the comfort of your own home, and you can tell \emph{immediately} and \emph{effortlessly} if the person of interest is intrigued in the conversation, and in turn, you. In a really weird way, this is the most rewarding portion of a self-monitoring communication strength- the online reward portion.
\par
Two specific examples that I can cite would be the following; when I was in Iraq which was my third deployment, I had to explain to officers multiple times the situation we are facing with our networks. Many challenged me on my expertise which with my confidence in the subject I was easily able to overcome the challenge. However, with group talks that I attempted to do in my Computer Science club, I recognize that my skills were lacking and needed significant improvement before I could make a decent contribution to the club that would be worthwhile. Whilst publically speaking, I began to become self-concious since I wasn't confident in the subject, which then from my perception made me look relatively dumb and sort of incoherently rambling.
\end{document}\
