\documentclass[12pt]{article}
\usepackage{times}
\usepackage{setspace}
\doublespacing
\usepackage[margin=1in]{geometry}

\begin{document}
\title{Reflection Journal 2}
\par
There is quite a variety in ways I communicate with people in Personal and Professional contexts for both face-to-face and mediated forms. For example, when working on assignments- even writing this assignment, I typically have a conversation with people in a social software called \emph{Discord}. Discord can be used exquisitely for both Personal and Professional use. Discord is phenomenal for communicating during games, communicating ideas across and holding meetings; our Computer Science club uses it extensively. Internet Relay Chat (IRC) is another mode of communication I use in a mediated form quite a bit, albeit it's mostly for support for software such as my Operating System on my computers, or specific software for that Operating System. For personal communication, I \emph{must} be physically at school for, since the synchronous communication for me is overwhelmingly necessary. Not being able to ask a Professor questions, or be able to interact with either my voice immediately when I don't have solid clarification on what is being asked of me, or to build a circuit with my own hands completely ruins my educational experience. \emph{SARS-CoV-2} in the Spring and Fall semesters of 2020 absolutely impacted my education since it defeated my drive for learning. I wasn't able to synchronously communicate with the Professors on subjects I cared deeply about.
\par
A Variety of skills that will enhance Interpersonal Communication would be first understanding yourself. Understand the particular needs that must be addressed to help you communicate properly. Previous trauma? Go to therapy regularly so your issues do not impact the communication with another person and turn an otherwise positive interaction to negative one. Have ADHD? If necessary, take medication, or dose up on caffeine prior just to keep you mentally focused on the communication at hand to stay focused. Think you have a poor standing with another person due to something you may have said or done? Ask the person for clarification, especially if that person has significant value to you.
\par
There is quite a variety of purposes and goals in interpersonal communication interactions. Each of them is a trade of value between each person. Whether it's acquiring knowledge from someone, acquiring affection \emph{romantic or aromantic}, wanting to share knowledge, etc. For example, this class itself is valuable to me since it helps me understand how to interact with various people better. I have value in other classes that are specific to my Major, since I hold a lot of value in understanding how to build circuits or write software. Communicating with family a lot of us hold significant value since we value \emph{them}. 
\par
The diversity and ethical considerations in interpersonal interactions could consist of different medical or mental disabilities, language or cultural differences, generational life experience, quality of life differences growing up between each individual, etc. The diversity between people in interpersonal interactions can be quite extreme, \emph{lack} of diversity would honestly be pretty impressive. 
\end{document}
