\documentclass[12pt]{article}
\usepackage{times}
\usepackage{setspace}
\doublespacing
\usepackage[margin=1in]{geometry}
\begin{document}
\title{Reflection Journal 10}
% 1. Consider the variables of “Why We Form Relationships” (pgs. 260-266).
%
%  -  Which variables played a role in forming this relationship?
%  -  How do these variables function now that you have a more established relationship?
\par
The variables for this relationship are quite extensive. It initially was \emph{Appearance} and \emph{Proximity} playing as the primary variables, being I was (and am) quite attracted to her. The beginning of our relationship was that I asked her out after our Trigonometry class, which she gently declined since she's currently in a long term relationship. These variables still play pretty heavily, she's still absolute eye candy, and I still share classes with her (albeit now it's all Electronics Engineering). However, I now consider her one of my closest friends because the new variables that have bloomed from our relationship are \emph{Similarity}, from sharing the same career passions, political & religious views, music tastes, etc. Additionally I would say \emph{Competency} plays a major role in our relationship. She enjoys keeping me around for in-depth computer and circuit knowledge, whereas I rely heavily on her for complex mathematical support which she excels at.
% 2. Discuss your relationship in terms of “Knapp’s 10 Stages of Relational Development” (pgs. 266-273). *Note: You do not have to discuss all ten stages. Only discuss those that you know your relationship has experienced.
\par
The stages that we have experienced together would be \emph{Initiating}, \emph{Experimenting}, and \emph{Intensifying}. Unfortunately, this will be the apex of our relationship. For Initiating, I was the one that began our first conversation ever, which was me asking her out for coffee. In Experimenting, we learned that we are both from the west coast in relatively rich areas, albeit though her family is \emph{significantly} far richer (they own vineyards in Napa Valley, and are leading engineers at Tesla). As far as Intensifying goes, we are constantly talking to each other through various means. Mostly through Snapchat, or Discord (She's talking to me whilst writing this sentence in Discord), or through Instagram. It's to a point where if I haven't talked to her for a day, I begin to feel worried about her mental state.
% 3. Review the section titled “Dialectical Tensions” (pgs. 273-278).
%
%  -  Give an example of a time this relationship experienced an internal dialectical tension.
%  -  Give an example of a time this relationship experienced an external dialectical tension.
\par
The strongest external dialectical tension we share would be conventionality-uniqueness. I'm honest to myself about my attraction to her, which can cause stirring within our relationship. This is difficult to contain as well, being she's such an incredibly intriguing person, having in-depth conversations with her is incredibly filling brain food. For internal dialectical tension, I would say that we share connection-autonomy dialectic. I want to have a closer relationship, and she is happy where it is (for obvious reasons, being she is in a romantic relationship), but I don't think that spending time together platonically outside of school is that big of a deal.
% 4. Review the section titled “Repairing Damaged Relationships” (pg. 284-287).
%
%  -  List two types of transgressions this relationship has experienced.
%  -  Explain how this relationship was repaired after these transgressions.
\par
Two types of transgressions our relationship has experienced would be \emph{Problematic Emotions}, and \emph{Verbal Hostility}. Our relationship was repaired from the former by her re-outlining her boundaries, and that she took something I said as being flirtatious, which I needed to clarify it wasn't at all what I was intending, which she then forgived me for since she saw her mistake-- yet also felt satisfied in restating her boundaries. For the latter, it was repaired after she apologized for exploding on me when I messaged her about some squirrel facts at 9am, when her professor did a major boundary breach and state HIPPA and PII information in front of the entire class.
\end{document}
