\documentclass[12pt]{article}
\usepackage{times}
\usepackage{setspace}
\doublespacing
\usepackage[margin=1in]{geometry}
\begin{document}
\title{Observation Exercise}

% What dynamics do you see between the people you're observing?
% What sort of relationship are you observing - parent/child, siblings, friends, a married couple, etc.
% What transpires in the interaction?
% What do you hear and see?
% What can you tell about the relationship from what is said. And, what can you tell about the relationship by what IS NOT said? And lest you think this is eavesdropping, you're functioning as a social science researcher!

% Two students, female, TTU

% Dynamics?

\par{\textbf{Observation 1}}
\par
The dynamics between the couple I am observing are quiet and focused on their assignment. They look like third year students from Texas Tech University that are either friends, or fellow students within the same class. The only thing that transpired in this interaction was quick comments about the assignment. I hear very quiet conversation, as if they don't want to bother anyone in the coffee shop, and see them intently working away on an assignment. I can't really tell what is being said in the conversation since they are speaking so quiet, and the noise from the road is so loud, but their conversation was definitely only about school work.
% Two dudes at the bar
\par{\textbf{Observation 2}}
\par
The dynamics between this group of people are energetic, happy, and engaged. They appear to be strangers, but enjoy talking about sports teams, and are comparing American football to military tactics. I see them actively watching the football game on the television whilst talking to random people coming up to the bar, and the bar tenders.
\par{\textbf{Observation 3}}
\par
% Couple with dog
The dynamics between this couple appears to be a date, and looks quite intimate. They are drinking wine and beer, and brought their dog out with them. They are also mentioning something about harassment which I think has something to do with the dog, and the dog growing bigger. A lot of the conversation in fact has to do with the dog, since random people keep coming up asking about the dog and if they can pet it. I can see that they are very relaxed and enjoying the night with each other and their dog. A few more people have joined them, and it seems like they are military couples joining in, possibly fellow shop members. They are talking about their trips to Korea, possibly being stationed there together.
\par{\textbf{Observation 4}}
\par
% Group of women
The dynamics between this group seems like it's a group of close friends going out on a wine date. They appear to all be very close with each other and possibly haven't hung out with everyone in a while. Everyone seems very engaged in the conversation and seemingly taking turns talking instead of talking over each other. They are joyful, and laughing every now and then so the conversation's back story must be quite intriguing. I can tell that this relationship is an interconnection of close friends.
\par{\textbf{Observation 5}}
\par
% Parents with kid
The dynamics between this group is parents with their daughter. The mother seems to be a teacher for one of the public schools here, and the dad is possibly an athletic coach. The conversation appears to be them either congratulating their daughter, or trying to push her in a direction to improve her grades. They are oriented in a way that both of the parents can look at their daughter to talk to her with proper eye contact. In a weird way, it almost looks like an interview to a job. It is very hard to discern what they are speaking of specifically however, since they talk so quiet in an area where everyone else likes speaking loud. I can tell that the conversation is specifically geared towards their daughter however, and maybe some chat about work on the side.
\end{document}
